---
title: "main_tutorial"
author: "William Medwid"
date: "11/24/2020"
output: html_document
---

## Welcome to the Flair team!

Here, we'll look at all of the more difficult aspects of how Flair works.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Concept 1: S3 Classes

If you're not yet familiar with the general concepts of OOP (Object Oriented Programming), research those first.

S3 classes are a basic form of class, allowing for three main features: Encapsulation, Inheritance, and Polymorphism.

Encapsulation - By wrapping up code in neat classes, the code becomes much more usable.

Inheritance - Allows code to be easily shared among objects.

Polymorphism - Allows functions to take multiple types of objects as input and output.

Many basic functions make use of S3 classes without the user ever needing to know. For example, you might think mean() is just a single function that can take nearly any class as input. However, we can run the following code to see that there are separate functions making up mean().

```{r}
methods(mean)
```

Each instance of mean takes the form mean.class, where class is the type class of data we're taking the mean of. An R object can have multiple classes, defined by a vector of class attributes. Generic functions like mean are very simple, like mean:

```{r}
mean <- function (x, ...) {
   UseMethod("mean", x)
}
```

UseMethod will look through each class x has, and if there's a method with the name mean.class, it calls that function.

Here are a few examples of how to assign a class attribute to a variable:

```{r}
x <- 1
attr(x, "class") <- "foo"
x
```

Or, to do the same in one line:

```{r}
x <- structure(1, class = "foo")
x
```

The recommended way to do this, though is to assign class(x)

```{r}
x <- 1
class(x) <- "foo"
x
```

Since x has the class foo, any generic function we assign will be treated as the generic for x. This simple achievement makes coding in R much easier because otherwise we would have to memorize a different function name, like mean.numeric or mean.date for every class. 

```{r}
mean.foo <- function(x){
  return(x+10)
}

mean(x)
```

## With_flair

S3 classes are used in Flair to make the with_flair class. This class has two methods: knit_print.with_flair, and print.with_flair. With_flair objects are generated from the decorate() function (the exact code for how they get generated is in decorate_chunk and decorate_code, which will be covered later.)

print.with_flair: If the editor isn't open, it returns nothing. Otherwise, it generates a temporary html file, modifies the input variable, and then calls viewer() so the HTML file shows  up as a sample in the viewer window. The code below follows the same structure, without the steps that modify the contents of x.

First, creating a temporary directory
```{r, creating_directory} 
tempDir <- tempfile()
dir.create(tempDir)
htmlFile <- file.path(tempDir, "index.html")
```

Then, modifying (or in this case, establishing) the input variable x. 
```{r, writing_file}
x = c("Testing ", "testing", "testing some more", "and even more testing")
```

</br> is the newline symbol in HTML, so one of the modifications made is to add it to the end of every line of code. The other modification made is to apply prep_source, which makes slight alterations depending on the document output type. It looks like prep_source isn't complete for all document types yet. 
```{r}
x <- stringr::str_c(unlist(x), collapse = "</br>")
```

Then, we write the lines of x to the HTML file.
```{r}
writeLines(x, htmlFile)
```

And finally, create a viewer to display the temporary HTML file.
```{r, viewing_file}
editorIsOpen <- tryCatch({ #This part ensures the code won't run when knitting, but will run in Rstudio.
    rstudioapi::getSourceEditorContext()
    TRUE
  }, error = function(e) FALSE)

if(!editorIsOpen){
  viewer <- getOption("viewer")
  viewer(htmlFile)
}
```

Remember that for this function, x is a variable with the class with_flair, which has (essentially) the structure of a list of lines of code, similar to the list of strings used in the example above. In print.with_flair, the lines aren't strings, but have the type "source" (at least, any that aren't of type "source" are removed).


To understand knit_print.with_flair, we'll first have to get to know the normal knit_print function.


